\textit{Associations between chlorophyll \emph{a} and various microcystin-LR health advisory concentrations}

### 2016-01-29 manuscript/f1000_submission/manuscript.Rmd
submission with archived DOI

#Software and Data Availability
Data and Latest Source Code: [https://github.com/USEPA/microcystinchla](https://github.com/USEPA/microcystinchla)

Archived data and source code at time of publication: []()

@@

#Author Contributions
JH and BK conceived of and conducted the analysis.  Both authors reviewed the results and contributed to writing the manuscript.

#Competing Interests
No competing interests were disclosed.

#Grant Information
The author(s) declared that no grants were involved in supporting this work.

>>>>

#Software and Data Availability

Data and Latest Source Code:
[https://github.com/USEPA/microcystinchla](https://github.com/USEPA/microcystinchla)

Archived data and source code at time of publication: [http://dx.doi.org/10.5281/zenodo.45317](http://dx.doi.org/10.5281/zenodo.45317)

@@

#Author Contributions

JH and BK conceived of and conducted the analysis.  Both authors reviewed the results and contributed to writing the manuscript.

#Competing Interests

No competing interests were disclosed.

#Grant Information

The author(s) declared that no grants were involved in supporting this work.

### 2016-01-29 manuscript/f1000_submission/manuscript.tex
submission release for DOI minting.
submission with archived DOI

\textbf{Keywords:}

@@

Archived data and source code at time of publication: \href{}{}

>>>>

\textbf{Keywords: }
Harmful Algal Blooms;
Cyanotoxins;
National Lakes Assessment;
Conditional Probability Analysis;
Cyanobacteria;

@@

Archived data and source code at time of publication:
\href{http://dx.doi.org/10.5281/zenodo.45317}{\url{http://dx.doi.org/10.5281/zenodo.45317}}
